\section{Test of the Basic Requirements}
This section discusses whether the basic requirements stated in section \ref{sec:basic_req} are fulfilled or not. 

\subsection{Test of  \autoref{req:dsp}}
In all cases, the requirement \ref{req:dsp} is fulfilled since all the effects are coded in Assembly.


\subsection{Test of  \autoref{req:speed}}
In the Appendix \ref{app:effect_run_time}, the runtime of the reverb effect, which gives the elapsed time from the moment a new sample arrives until it is loaded for output, has been tested. \\
Figure \ref{fig:reverb_time_test} shows that only 2.23 microseconds are needed to run the \gls{reverb} effect. \\
Figure \ref{fig:flanger_time_test} shows that the flanger runtime is 2.25 microseconds. \\
Figure \ref{fig:eq_time_test} shows that the equalizer runtime is 2.35 microseconds. \\
The results show that the runtimes of the effects are clearly faster than the sampling time of the \gls{dsp} which is 23 microseconds. \\
It can be concluded that the effects are real-time, faster than the sampling frequency thus the requirement \ref{req:speed} is fulfilled. \\

\subsection{Test of \autoref{req:SNR}}
\autoref{req:SNR} states that the \gls{snr} of the final system must be larger than the \gls{snr} in the guitar. In \autoref{app:preamp_frequency_response} the \gls{snr} in the guitar is tested to be \SI{70.06}{\decibel}. In \autoref{sec:dsp_description} it is seen that the \gls{adc} on the TMS320C5515 eZdsp development board has a \gls{snr} of \SI{93}{\decibel}. A test was made in \autoref{app:test:snr_dsp}, to measure the \gls{snr} in the \gls{dsp}. It was found that the \gls{dsp} has a \gls{snr} of \SI{39.91}{\decibel}, which is lower than the guitars \gls{snr}. Thus the requirement cannot be approved. 

\subsection{Test of \autoref{req:power}}
\autoref{req:power} states that the maximum output of any of the effects must not be larger than what the \gls{dac} can represent. The \gls{dac} on the TMS320C5515 eZdsp development board has a full scale output voltage of 0.5 V$_{RMS}$ \citep{TLV320AIC3204}. An input gain function has been implemented in the \gls{dsp} to be able to decrease the output after the effect, if the output is larger than what the \gls{dac} can represent. Thus the requirements is approved.

\subsection{Test of \autoref{req:power2}}
\autoref{req:power2} states that the product shall be powered by a \SI{9}{\volt} supply. The TMS320C5515 eZdsp development board is powered by USB, which is a \SI{5}{\volt} supply. Thus the requirement is not approved.

\subsection{Test review of the Basic Requirements}
In this subsection, a short review will be shown of the Basic test.

\begin{table}[H]
\centering
\caption{Recap of the requirements fulfilments for the Basic test}
\label{test_of_basic_table}
\begin{tabular}{|l|l|}
\hline
\rowcolor[HTML]{9B9B9B} 
\textbf{Requirement} & \textbf{Fulfilment State} \\ \hline
\textbf{\ref{req:speed}}    & \cmark                     \\ \hline
\textbf{\ref{req:speed}}    & \cmark                     \\ \hline
\textbf{\ref{req:SNR}}    & \xmark                     \\ \hline
\textbf{\ref{req:power}}    & \cmark                     \\ \hline
\textbf{\ref{req:power2}}    & \xmark                     \\ \hline
\end{tabular}
\end{table}
