\section{Conclusion}

It can be concluded that sound from a \gls{bc} is mostly said to be transferred through the bone, but research shows that the skin and rest of the auditory canal do have a big influence of the sound perception of the \gls{bc}. It was discovered in \autoref{sec:bonepaths} that the sound travelling path through the skin attenuate the sound approximate \SI{20}{\decibel} in the \gls{bc} frequency range. It was also discovered that the sound are not only going through the bone, but also through the rest of the auditory canal. The bone and skin in the ear canal is radiating sound intro air which make the eardrum to move. The ossicular chain transfer the air born sound to the cochlear but the chain is also affected it self by vibration in the skull, which makes the bone to move. The fluid on the inside of the skull is also affected by the skull vibration and transfer sound through the cochlear fluid canal.  

It can be concluded that the excitation of the \gls{bm} from \gls{bc} sound is similar when using \gls{ac}. Study have shown that \gls{bc} sound can be successfully cancelled with present of \gls{ac} sound where only the phase and amplitude is manipulated in the \gls{ac}. 

It can be concluded that the fundamental frequency of the voice lays down in the the octave band of \SI{125}{\hertz} and \SI{250}{\hertz} but only \SI{5}{\percent} of the speech intelligibility are within those two octave band. The throat, mouth and the nose is a transfer system which change the sound from the glottal in such way that the frequency range for speech goes from \SI{20}{\hertz} to \SI{7}{\kilo\hertz}, where the highest speech intelligibility lays in the octave band of \SI{500}{\hertz}, \SI{1}{\kilo\hertz}, \SI{2}{\kilo\hertz} and \SI{4}{\kilo\hertz}. The necessary frequency range for good speech intelligibility is therefore from \SI{355}{\hertz} to \SI{5.68}{\kilo\hertz} when including the outer limit of the octave band.

It can be concluded that the Radioear B71 does not cover the full frequency area that is needed for good speech intelligibility but cover the most. The problem with the B71 is that the distortion from \SI{1}{\kilo\hertz} and below is higher than \SI{10}{\percent} and therefore the B71 is concluded to be infeasible for communication use. The newer model, Radioear B81 are therefore analysed and it can be concluded that the B81 is feasible for communication, since the \gls{best} principle makes the frequency range wider because of lower distortion. In fact the frequency range from \SI{355}{\hertz} to \SI{5.68}{\kilo\hertz} is covered with the B81 and the distortion is generally less than \SI{4}{\percent} and in most of the interesting frequency range the distortion is lower than \SI{1}{\percent}.

It is concluded that the \gls{bc} for this project will be the Radioear B81 and the research frequency shall at least cover the frequency range from \SI{355}{\hertz} to \SI{5.68}{\kilo\hertz} to cover more than \SI{90}{\percent} for the speech intelligibility frequency range. The frequency range is allowed to be wider but not smaller to ensure high probability for high speech intelligibility.