\section{Relation of Airborne and Bone Induced Sound}
For a considerable amount of time, there has been an interest in characterizing the way in which \gls{bc}-induced sound is perceived in comparison to \gls{ac} sound. In order to do so, knowledge about the anatomical and physiological aspects that contribute to the perception of sound is necessary.
The pathways that contribute to \gls{bc} causing the excitation in the \gls{bm} have been described in \ref{sec:bonepaths}. A relatively recent summary can also be found in \citep{dauman_2013}.\\
In \citep{bekesy_1932}, the author is successfully cancelling the perception of a bone induced tone on a human subject with airborne sound. In order to do so, phase and amplitude of the airborne sound were manipulated. This led to the assumption that inducing sound via the bones results in similar patterns on the \gls{bm} as airborne sound \citep{stenfelt_2007}.
In \citep{lowy_1942}, this cancellation of airborne and bone induced sound is investigated in greater detail. 

The electrical cochlear response has been measured on anesthesized cats and guinea pigs, while an airborne tone was cancelled with a bone induced tone in a frequency range from \SIrange{250}{3000}{\hertz}. These experiments showed that when the signal parameters are adjusted for cancellation at one position of the cochlea, the cancellation is also achieved when measuring on another position. This again suggests that the excitation patterns on the \gls{bm} caused by \gls{bc} are fairly similar to those caused by \gls{ac} sound. More recently, \citep{stenfelt_2007} conducted cancellation experiments with multiple tones. This is motivated by the observation of phenomena in different studies, which points towards differences between \gls{ac}- and \gls{bc}-induced sound in the context of otoacoustic emissions and auditory brainstem response. 
Stenfelt \citep{stenfelt_2007} is presenting three test subjects with cancellation tasks, some of which involve more than one tone. Some minor deviations from the expected behaviour regarding the phase and amplitude parameters for cancellation were observed and noted down during this test. However, no statistically significant tendencies can be obtained from the test data, which would indicate that the auditory system does not behave like a linear system for \gls{ac} and \gls{bc} at the investigated frequencies (\SI{700}{\hertz},\SI{1100}{\hertz}, \SIrange{40}{60}{\decibel}HL).
Furthermore, the author alludes that the cancellation parameters are fairly sensitive to movements of the head and jaw by the subjects. 