\chapter{Computing the Beamwidth}\label{appendix:beamwidth}
In this appendix the beamwidth calculation software will be explained briefly. The goal of the software is to determine the $-n$\si{\decibel} beamwidth of any speaker known polar response.

\section*{Materials}
To calculate the $-n$\si{\decibel} beamwidth, the following materials are used:
\begin{itemize}
\item MATLAB 2017b (PC - software)
\end{itemize}


\section*{Calculation procedure}
The $-n$\si{\decibel} beamwidth calculation software is built as a search function. It compares main axis measurement value with a measurements from a given angles and finds the first frequency where the \gls{spl} difference between front measurement and the measurement from the given angle is $n$\si{\decibel} or bigger. The following steps are to done in order to be able to calculate the $-n$\si{\decibel} beamwidth.

\begin{enumerate}
\item The materials are set up as in \autoref{fig:measurement_setup}.
\item The polar response is measured according to \autoref{appendix:measuring_manual}
\item The acoustical center of the speaker is found according to \autoref{sec:ac_center}
\item  The speaker is moved such that the acoustic center stays in the same point. 
\item The polar response is measured again according to \autoref{appendix:measuring_manual}
\item All transfer functions are calculated from the polar response.
\item $n$ is chosen and the  $-n$\si{\decibel} beamwidth calculation software is executed.
\end{enumerate}


\section*{The MATLAB function}
\includeCode{minus_ndB_beamwidth.m}{matlab}{1}{52}{The $-n$\si{\decibel} beamwidth search software}{code:minus_ndB_beamwidth}{./code/beamwidth/}
